\section{Results}

The technique described in this paper was implemented in ABC \cite{abc-link}. It applies algebraic rewriting to the AIG and generates the polynomial signature. The experiments include gate-level rewriting of Carry-Save-Adder (CSA) multipliers up to 512 bits. The results are compared with \textit{functional extraction} \cite{ciesielski2015verification}.
The results show that the proposed technique is more efficient than the state-of-the-art technique for extracting the polynomial expressions for the CSA multipliers. The experiments were conducted on a PC with Intel(R) Xeon CPU E5-2420 v2 2.20 GHz x12 with 32 GB memory.

The results of applying AIG-based algebraic rewriting to pre-synthesized and post-synthesized CSA multipliers are shown in Table \ref{tbl:pre} and Table \ref{tbl:post}, respectively. The gate-level multipliers are taken from \cite{ciesielski2015verification}. Runtime and memory usage of \textit{functional extraction} \cite{ciesielski2015verification} are shown in columns 2 and 3, and the results of the proposed approach are shown in columns 4 and 5. The bit-width varies between 8 and 256 bits\footnote{512-bit post-synthesized multipliers are not reported in \cite{ciesielski2015verification}.}. First, we can see that the runtime of the proposing approach is lower than a second for both the pre- and post-synthesized CSA multipliers for any bit-width. At the same time, memory usage has been reduced on average 60\%, compared to \textit{function extraction} \cite{ciesielski2015verification}. Finally, the complexity of extracting the polynomial expression using functional extraction is increased when the multipliers are synthesized. For example, extracting post-synthesized 256-bit multiplier using functional extraction requires 9x more runtime and more memory. However, using the proposed approach, the runtime of extracting pre- or post-synthesized multipliers are almost the same.

\input{../table/pre-syn.tex}
\input{../table/post-syn.tex}

%\input{../table/booth-mult.tex}
