
%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\documentclass[runningheads,a4paper]{llncs}
\documentclass[journal]{IEEEtran}
\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{pst-3dplot}
\usepackage{algorithmicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{multirow}
\usepackage{url}
\newcommand{\rom}[1]{\uppercase\expandafter{\romannumeral #1\relax}}

%\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
%\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
%\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
%\newcommand{\keywords}[1]{\par\addvspace\baselineskip
%\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

%\mainmatter  % start of an individual contribution

% first the title is needed
\title{Fast Algebraic Rewriting Based on And-Inverter Graphs}

% a short form should be given in case it is too long for the running head
%\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
%\author{Cunxi Yu\inst{1}%
%\thanks{}%
%\and Maciej Ciesielski\inst{1} \and Alan Mishchenko\inst{2}}
%\institute{ECE Department, University of Massachusetts, Amherst \\Amherst, MA 01003\    \\ \email{ycunxi@umass.edu},\\
%\and
%ECE Department, University of California, Berkeley, \\ Berkeley, CA 94720\   \\  \email{alanmi@eecs.berkeley.edu}\\
%}

\author{\IEEEauthorblockN{Cunxi~Yu,~\IEEEmembership{Student Member,~IEEE}, Maciej Ciesielski,~\IEEEmembership{Senior Member,~IEEE}, and \\Alan Mishchenko,~\IEEEmembership{Senior Member,~IEEE}}\\
\thanks{C. Yu and M. Ciesielski are with the Department of Electrical and Computer Engineering at University of Massachusetts, Amherst, MA, 01003, USA (ycunxi@umass.edu, xiangyuzhang@umass.edu, ciesiel@ecs.umass.edu).}
\thanks{A. Mishchenko is with EECS Department at University of California, Berkeley, Berkeley, CA 94720 (alanmi@berkeley.edu)}
}



%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%


\maketitle




\begin{abstract}
%Based on the successes of arithmetic verification using computer algebra method, this paper presents a fast computer algebraic rewriting technique based on And-Inv-Graphs (AIGs). The technique significantly improves the performance of the existing methods. 
Constructing algebraic polynomials using computer algebra techniques is believed to be state-of-the-art in analyzing gate-level arithmetic circuits. However, the existing approach applies algebraic rewriting directly to a gate-level netlist, which has potential memory explosion problem. This paper introduces an algebraic rewriting technique based on the And-Inverter Graph (AIG) representation of gate-level designs. Using AIG-based cut-enumeration and truth table computation, an efficient order of algebraic rewriting is identified, resulting in dramatic simplifications of the polynomial under construction. An automatic approach, which further reduces the complexity of algebraic rewriting by handling redundant polynomials, is also proposed. 
%Experimental results specially target on integer multipliers, including CSA-Array multiplier and Booth multipliers, up to 512-bit. The results show that the proposing approach significantly improves the performance of rewriting on post-synthesized multipliers, and overcomes the limitation of verifying Booth multipliers using compute algebraic method. 
%\Keywords{Formal verification, AIGs, functional verification, arithmetic circuits, computer algebraic}
\end{abstract}


\input{intro.tex}
\input{related-work.tex}
\input{approach}
\input{results}
\maketitle

\IEEEdisplaynontitleabstractindextext

\IEEEpeerreviewmaketitle

\vspace{-3mm}

\section{Conclusion}
This paper presented a method to improve the efficiency of algebraic rewriting used in arithmetic verification. The method is based on the representation of the Boolean network called an And-Inverter Graph (AIG). This approach allows for formal verification of practical multipliers that are heavily optimized and mapped using 14nm technology library. Another contribution of the paper is a technique that automatically detects redundant polynomials to reduce the complexity of algebraic rewriting.


\section*{Acknowledgment}
This work was supported by an award from National Science Foundation, No. CCF-1319496 and No. CCF-1617708. The co-author affiliated with UC Berkeley was supported in part by NSA grant ``Enhanced equivalence checking in
crypto-analytic applications''.



\bibliographystyle{IEEEtran}
\bibliography{/Users/cunxiyu/Documents/Texshop/cunxi_bib/verification_ycunxi,/Users/cunxiyu/Documents/Texshop/cunxi_bib/synthesis}

\end{document}

