
%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\documentclass[runningheads,a4paper]{llncs}
\documentclass[journal]{IEEEtran}
\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{pst-3dplot}
\usepackage{algorithmicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{multirow}
\usepackage{url}
\newcommand{\rom}[1]{\uppercase\expandafter{\romannumeral #1\relax}}

%\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
%\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
%\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
%\newcommand{\keywords}[1]{\par\addvspace\baselineskip
%\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

%\mainmatter  % start of an individual contribution

% first the title is needed
\title{Fast Algebraic Rewriting based on And-Inv-Graphs}

% a short form should be given in case it is too long for the running head
%\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
%\author{Cunxi Yu\inst{1}%
%\thanks{}%
%\and Maciej Ciesielski\inst{1} \and Alan Mishchenko\inst{2}}
%\institute{ECE Department, University of Massachusetts, Amherst \\Amherst, MA 01003\    \\ \email{ycunxi@umass.edu},\\
%\and
%ECE Department, University of California, Berkeley, \\ Berkeley, CA 94720\   \\  \email{alanmi@eecs.berkeley.edu}\\
%}

\author{\IEEEauthorblockN{Cunxi~Yu,~\IEEEmembership{Student Member,~IEEE,}, Maciej Ciesielski,~\IEEEmembership{Senior Member,~IEEE,} and \\Alan Mishchenko ,~\IEEEmembership{Member,~IEEE,}}\\
\thanks{C. Yu and M. Ciesielski are with the Department of Electrical and Computer Engineering at University of Massachusetts, Amherst, MA, 01003, USA (ycunxi@umass.edu, xiangyuzhang@umass.edu, ciesiel@ecs.umass.edu).}
\thanks{A. Mishchenko is with EECS Department at University of California, Berkeley, Berkeley, CA 94720 (alanmi@eecs.berkeley.edu)}
}



%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%


\maketitle




\begin{abstract}
%Based on the successes of arithmetic verification using computer algebra method, this paper presents a fast computer algebraic rewriting technique based on And-Inv-Graphs (AIGs). The technique significantly improves the performance of the existing methods. 
Computer algebra method with polynomial representations is believed to be the state-of-the-art technique for analyzing gate-level arithmetic circuits. However, the existing approach applies algebraic rewriting directly on the gate-level netlist, which has potential memory explosion problem. In this paper, an algebraic rewriting technique, through the AIGs of the gate-level design, is introduced. Using the AIG-based structural hashing, an efficient order of rewriting, that provides the maximum polynomial reductions during the rewriting process is identified. This approach is based on detecting the pairs of Majority3 and XOR3 functions in AIGs. An automatic approach which reduces the complexity of algebraic rewriting and generates redundant polynomials is proposed. 
%Experimental results specially target on integer multipliers, including CSA-Array multiplier and Booth multipliers, up to 512-bit. The results show that the proposing approach significantly improves the performance of rewriting on post-synthesized multipliers, and overcomes the limitation of verifying Booth multipliers using compute algebraic method. 
%\Keywords{Formal verification, AIGs, functional verification, arithmetic circuits, computer algebraic}
\end{abstract}


\input{intro.tex}
\input{related-work.tex}
\input{approach}
\input{results}
\maketitle

\IEEEdisplaynontitleabstractindextext

\IEEEpeerreviewmaketitle

\vspace{-3mm}

\section{Conclusion}
We propose an approach presented that aims at improving the efficiency of algebraic rewriting for arithmetic verification, using a Directed-Acyclic-graph (DAG) representation of the Boolean network, called And- Inverter-Graph (AIG). With this approach, we address the formal verification problem of practical multipliers that are heavily optimized and mapped using 14nm technology library. Also, an approach that automatically detects redundant polynomials to reduce the complexity of algebraic rewriting is proposed.


\section*{Acknowledgment}
This work was supported by an award from National Science Foundation, No. CCF-1319496 and No. CCF-1617708. 



\bibliographystyle{IEEEtran}
\bibliography{/Users/cunxiyu/Documents/Texshop/cunxi_bib/verification_ycunxi,/Users/cunxiyu/Documents/Texshop/cunxi_bib/synthesis}

\end{document}
